---
title: "Reproducible data peer asignment 1"
date: "3 May 2016"
output: html_document
---

## Loading and preprocessing the data

Firstly we load the data and make some basic transformations for further analysis.
```{r}
require(data.table)
# setwd("/Users/khispa/Data Sciense Specialization/Reproducible_research")
setwd("C:/Users/m.diaz.fernandez/Documents/Cosas mias/R/Rep_research")
activity <- read.csv("activity.csv")
summary(activity)
activity <- data.table(activity)
```

## What is mean total number of steps taken per day?


```{r}
setkey(activity, date)
act_group <- activity[,sum(.SD$steps), by=date]
hist(act_group$V1)
mean(act_group$V1)
median(act_group$V1)
```
The mean of number of steps per day is `r mean(act_group$V1)` and the median is `r median(act_group$V1)`.

## What is the average daily activity pattern?

```{r}
act_average <- activity[,mean(.SD$steps, na.rm = TRUE), by=date]
plot.ts(act_average$V1)
max <- activity[which(activity$steps==max(activity$steps)&!is.na(activity$steps)),]
```
The interval with the maximum number of steps was `r max[1,3]` in `r max[1,2]` with `r max[1,1]` steps. 

## Imputing missing values

Total number of "NA":
```{r}
dim(activity[which(is.na(activity$steps)),])[1]
```

Strategy to deal with Na´s in the dataset. We take the most naive approach, id est, consider that if data is missing there were 0 steps in that 5 minute interval.
```{r}
activity_no_na <- activity
activity_no_na$steps[which(is.na(activity_no_na$steps))] <- 0
act_group2 <- activity_no_na[,sum(.SD$steps, na.rm = TRUE), by=date]
hist(act_group2$V1)
mean(act_group2$V1)
median(act_group2$V1)
```
The new mean of number of steps per day is `r mean(act_group2$V1)` and the median is `r median(act_group2$V1)`.

## Are there differences in activity patterns between weekdays and weekends?

```{r}
activity_no_na$date <- as.Date(activity_no_na$date)
activity_no_na$week <- as.POSIXlt(activity_no_na$date)$wday
activity_no_na$weekd <- ifelse(activity_no_na$week %in% c(0,6), 0,1)
```

